### 2022-05-30 chapters/04-chapter-4.tex
txs auto checkin

\subsubsection{Kasus SI1}
Pada kasus S

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.75\textwidth]{resources/ch4/resource/1-cpu.png}
	\caption{Penggunaan CPU pada kasus SI1}
	\label{result_cpu_1}
\end{figure}

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.75\textwidth]{resources/ch4/resource/1-mem.png.png}
	\caption{Penggunaan CPU pada kasus SI1}
	\label{result_cpu_1}
\end{figure}

>>>>

\subsubsection{Kasus SI1}
Dari gambar \ref{result_cpu_1} dan \ref{result_mem_1} terlihat bahwa

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/ch4/resource/1-cpu.png}
	\caption{Penggunaan CPU pada kasus SI1}
	\label{result_cpu_1}
\end{figure}

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/ch4/resource/1-mem.png}
	\caption{Penggunaan Memory pada kasus SI1}
	\label{result_mem_1}
\end{figure}
